---
output:
  word_document: default
  html_document: default
  pdf_document: default
---
## Statistical report
```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```
This document is a statistical report on the dataset used in our project.\
The dataset contains anonymous ratings(-10 to 10) provided by a total of 41,000 
users. Train file contains 1.1 million ratings for 139 jokes.\

Here we load the data and create the dataframe.
```{r}
library("ggplot2")
trainSet <- read.csv("train.csv")
df <- data.frame(trainSet)
```
Here is a histogram representing distribution of the grade. The distribution is
little skewed to the right.
```{r, fig.align='center', fig.height=7, fig.width=7}
hist(df$Rating,main = "Distributions of ratings", xlab = "Rating")
```
Here is a histogram representing average joke rating distribution. Average joke 
rating ranges from -3 to 4, the most  popular are within [1.5, 2]. The distribution 
of average ratings is a little skewed to the right.
```{r, fig.align='center', fig.height=7, fig.width=7}
average_ratings <- aggregate(df$Rating ~ df$joke_id, df, mean)
hist(average_ratings$`df$Rating`,ylim=c(0,25), breaks = 20, main = "Average joke rating distribution", xlab = "Rating")
```
Here is a histogram representing number of ratings distribution. As we can see, 
the popularity of jokes is different. While some jokes have more than 25,000 ratings, 
others do not even reach 1000 ratings.
```{r, fig.align='center', fig.height=7, fig.width=7}
ratings_numbers <- aggregate(df$Rating ~ df$joke_id, df, length)
plot(ratings_numbers, type = "h", breals = 139, main = "Number of ratings distribution", xlab = "Joke id", ylab = "Number of ratings")
```
Here is a histogram representing standart deviations of jokes ratings distribution.
As we can see, the standard deviations form a normal distribution. From this we can 
conclude that the ratings of jokes are compatible.
```{r, fig.align='center', fig.height=7, fig.width=7}
standart_deviations <- aggregate(df$Rating ~ df$joke_id, df, sd)
hist(standart_deviations$`df$Rating`, xlim = c(4, 6.5),ylim=c(0,20), breaks = 20, main="Standart deviations distribution", xlab = "Standart deviation",
     ylab = "Jokes number")
```