---
output:
  word_document: default
  html_document: default
  pdf_document: default
---
## Statistical report
```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```
This document is a statistical report on the dataset used in our project.\
The dataset contains anonymous ratings(-10 to 10) provided by a total of 41,000 
users. Train file contains 1.1 million ratings for 139 jokes.\

Here we load the data and create the dataframe.
```{r}
library("ggplot2")
trainSet <- read.csv("train.csv")
df <- data.frame(trainSet)
```
Here is a histogram representing distribution of the grade. The distribution is
little skewed to the right.
```{r, fig.align='center', fig.height=7, fig.width=7}
hist(df$Rating,main = "Distributions of ratings", xlab = "Rating")
```
Here is a histogram representing average joke rating distribution. Average joke 
rating ranges from -3 to 4, the most  popular are within [1.5, 2]. The distribution 
of average ratings is a little skewed to the right.
```{r, fig.align='center', fig.height=7, fig.width=7}
average_ratings <- aggregate(df$Rating ~ df$joke_id, df, mean)
hist(average_ratings$`df$Rating`,ylim=c(0,25), breaks = 20, main = "Average joke rating distribution", xlab = "Rating")
```
Here is a histogram representing number of ratings distribution.
```{r, fig.align='center', fig.height=7, fig.width=7}
ratings_numbers <- aggregate(df$Rating ~ df$joke_id, df, length)
plot(ratings_numbers, type = "h", breals = 139, main = "Number of ratings distribution", xlab = "Joke id", ylab = "Number of ratings")
```